---
title: "Examen"
output: html_document
---

```{r}
install.packages("tidyverse")
```


```{r}
library(tidyverse)
```

```{r}
StackOverflow <- read.csv("survey_results_public.csv")
```


```{r}
StackOverflow
```





Exploratory Analysis



#1.- Do you contribute to open source projects?

```{r}
OpenSourceGraf <- ggplot(data = StackOverflow) + 
  geom_bar(mapping = aes(x = OpenSource, fill = OpenSource))

Pregunta1 <- OpenSourceGraf + theme (text = element_text(size=12)) + 
  ggtitle ("Do you contribute to open source projects?") +
  labs(x = "Contribuye en Open Source",y = "Cantitad")

Pregunta1
```

La gráfica anterior muestra el total de personas que participan y no participan en proyectos de Open Source.





#2.- In which country do you currently reside?

```{r}
StackOverflow %>% count(Country)

ggplot(data = StackOverflow) + 
  geom_bar(mapping = aes(x = Country))
```
La gráfica anterior muestra la cantidad de personas de cada país.





#3.- Are you currently enrolled in a formal, degree-granting college or university program?

```{r}

ggplot(data = StackOverflow) + 
  geom_bar(mapping = aes(x = Student, fill = Student)) + 
  theme (text = element_text(size=12)) + 
  ggtitle ("Are you currently enrolled in a formal, degree-granting college or university program?") +
  labs(x = "Es estudiante",y = "Cantitad")

```
En la gráfica anterior podemos observar si son estudiantes de tiempo completo, parte del tiempo o si no están estudiando.






#4.- Which of the following best describes your current employment status?

```{r}
ggplot(data = StackOverflow) + 
  geom_bar(mapping = aes(x = Employment, fill = Employment)) + 
  theme (text = element_text(size=12)) + 
  ggtitle ("Which of the following best describes your current employment status?") +
  labs(x = "Employment",y = "Cantitad")
```
En la gráfica anterior nos muestra el estado actual del empleo de las personas encuestadas.






#5.- Which of the following best describes the highest level of formal education that you’ve completed?

```{r}
ggplot(data = StackOverflow) + 
  geom_bar(mapping = aes(x = FormalEducation, fill = FormalEducation)) + 
  theme (text = element_text(size=12)) + 
  ggtitle ("Which of the following best describes the highest level of formal education that you’ve completed?") +
  labs(x = "Formal Education",y = "Cantitad")
```
Esta gráfica nos muestra hasta que grado escolar formal llegaron las personas que contestaron la encuesta.





```{r}
SETAP <- read.csv("Software Engineering Team Assessment and Prediction (SETAP) Project - Sheet1.csv")
```


```{r}
SETAP
```


#1.-How many observations per year?

```{r}
SETAP %>% count(year)

ggplot(data = SETAP) + 
  geom_bar(mapping = aes(x = year, fill = semester)) + 
  theme (text = element_text(size=12)) + 
  ggtitle ("How many observations per year?") +
  labs(x = "Año",y = "Observaciones") 
```





#2.- In which year and season the collection data process began?

```{r}
ggplot(SETAP, aes(x = year, y = semester, colour = year == "2012")) +
geom_point(position = position_jitter()) + 
  theme (text = element_text(size=12)) + 
  ggtitle ("In which year and season the collection data process began?") +
  labs(x = "Año",y = "Observaciones por semestre") 
```







#3.- How many observations the data shows per gender (male vs female) in total. And how many observations per gender (male vs female) is divided by year?

```{r}
ggplot(data = SETAP) + 
  geom_bar(mapping = aes(x = teamLeadGender, fill = teamLeadGender)) + 
  theme (text = element_text(size=12)) + 
  ggtitle ("How many observations the data shows per gender (male vs female) in total") +
  labs(x = "Genero",y = "Observaciones") 
```

```{r}
SETAP %>%
  filter(teamLeadGender == "F") %>%
  ggplot(aes(x = year, fill = semester))+ 
  geom_bar() + 
  theme (text = element_text(size=12)) + 
  ggtitle ("How many observations per Female is divided by year") +
  labs(x = "Año",y = "Observaciones") 
```

```{r}
SETAP %>%
  filter(teamLeadGender == "M") %>%
  ggplot(aes(x = year, fill = semester))+ 
  geom_bar() + 
  theme (text = element_text(size=12)) + 
  ggtitle ("How many observations per Male is divided by year") +
  labs(x = "Año",y = "Observaciones")
```






#4.- How many students are grouped by each team? And how many students are grouped by each team per semester and per year? (This question should show 3 graphs)

```{r}
ggplot(data = SETAP) + 
  geom_bar(mapping = aes(x = teamNumber, fill = teamLeadGender)) + 
  theme (text = element_text(size=12)) + 
  ggtitle ("How many students are grouped by each team?") +
  labs(x = "Equipo",y = "Observaciones por equipo") 
```

```{r}
ggplot(data = SETAP) + 
  geom_bar(mapping = aes(x = teamNumber, fill = semester)) + 
  theme (text = element_text(size=12)) + 
  ggtitle ("How many students are grouped by each team per semester") +
  labs(x = "Equipo",y = "Observaciones por equipo") 
```





#5.- What is the relationship between the number of commits (commitCount) and the total hours of coding deliverables (codingDeliveablesHoursTotal)? Can we infer a relationship? Could we define this relationship as positive or negative?



